Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-13 paper/sections/acknowledgements.tex
[ paper ] working on section three.

We thank Joe Leslie-Hurd for his support with \Metis prover. We also
acknowledge the work carried out by Alejandro G\'omez-Londo\~no~\cite{Gomez-Londono2015} used as the basis code for our \TSTP
parsing module.
% \improvement{We should consider thank Kanso and Anton, to provide
% us their thesis, discussion, and source code to compare with our
% work?}

Last but not least, we thankfully acknowledge
Andreas Abel and Chalmers University of Goteborg, Sweden for
inviting us to be part of the \Agda Implementors’ Meeting XXV where
we presented part of this paper.

>>>>

We thank Joe Leslie-Hurd for his support with its \Metis prover.
We also acknowledge the work carried out by Alejandro G\'omez-Londo\~no~\cite{Gomez-Londono2015} used as the basis code for our \TSTP
parsing module.

Last but not least, we thankfully acknowledge
Andreas Abel and Chalmers University of Goteborg, Sweden for
inviting us to be part of the \Agda Implementors’ Meeting XXV.
We honored to present part of the research in this paper.
